Enhancing Forecast Reconciliation: A Study of Alternative Covariance Estimators

### 2025-07-29 literature/paper_draft.qmd
Update paper_draft.qmd

@@

Regarding reconciliation strategies, we consider OLS, mint_shr (MinT with Shrinkage estimator), and mint_n (MinT with NOVELIST estimator). Note that the number of series is larger than the number of observations (560 compared to 96), hence the sample covariance matrix is not positive definite and will not be used.

>>>>

@Wickramasuriya2019-xq also argued that modelling spatial autocorrelations would be challenging as in the case of a large collection of time series. Reconciliation approaches have the advantage to implicitly model this spatial autocorreltion structure, especially when the MinT method is used.

@@

Regarding reconciliation strategies, we consider OLS, mint_shr (MinT with Shrinkage estimator), and mint_n (MinT with NOVELIST estimator). Note that the number of series is larger than the number of observations (560 compared to 96), hence the sample covariance matrix is not positive definite and will not be considered
